Predictors of frog survival following translocations - supplemental analyses

### 2022-11-01 code/translocation_survival_analysis_suppl.Rmd
Fix typos

### Description of dataset columns 
-  site_id: Unique 5-digit site identifier.  
-  site_id1: Assigned 5-digit site identifier for a collection of nearby sites utilized by a frog population.
-  translocation_id: Unique identifier for each translocation.  
-  visit_date: Date on which translocation/survey was conducted.  
-  survey_type: "translocation" or "cmr".  
-  period: "before" or "after" translocation.
-  year_translocate: Year in which translocation was conducted.  
-  year_capture: Year in which frog was captured.  
-  interval: Number of years between translocation and frog capture.  
-  pit_tag_ref: Unique PIT tag identifier.  
-  swab_id: Unique identifier for skin swab sample.  
-  bd_load: Bd infection intensity determined from skin swab sample, units are number of ITS1 copies * 80.

>>>>

### Description of dataset columns 
-  site_id: Unique 5-digit site identifier.  
-  site_id1: Assigned 5-digit site identifier for a collection of adjacent sites that are utilized by a frog population.
-  translocation_id: Unique identifier for each translocation.  
-  visit_date: Date on which translocation or survey was conducted.  
-  survey_type: "translocation" or "cmr".  
-  period: "before" or "after" translocation.
-  year_translocate: Year in which translocation was conducted.  
-  year_capture: Year in which frog was captured.  
-  interval: Number of years between translocation and frog capture.  
-  pit_tag_ref: Unique PIT tag identifier.  
-  swab_id: Unique identifier for skin swab sample.  
-  bd_load: Bd infection intensity determined from skin swab samples, units are number of ITS1 copies * 80.
